Robust Bayesian Analysis of Causal Inference Problems

### 2024-03-25 JASA-template.tex
Small update (Matthias).
update analysis

\begin{abstract}
%%% MT to TB: will try reduce abstract length slightly        
Causal inference using observational data is important in
many fields, including epidemiology, social science, economics, and many more.
The goal of causal inference is to find the treatment effect on the subjects
by identifying causal links between the variables and the outcome.
However, estimation of such causal links is extremely 
difficult because the treatment effects may vary from subject 
to subject. Unfortunately, modelling the underlying heterogeneity explicitly makes the 
problem practically unsolvable. Additionally, for high dimensional problems,
we often need to find a subset of 
explanatory variables to initiate the treatment. However, current variable selection methods
simply tend to maximise the predictive performance of the outcome model. This can be problematic when information and data are limited,
as the consequence of mistreatment can be harmful. 
So, in this paper, we develop a model for causal inference using
robust Bayesian analysis, to allow for abstention when selecting
explanatory variables.
Our robust Bayesian model uses a set of spike and slab priors 
through prior elicitation to obtain robust estimates for
both the treatment and outcome model. We are specifically interested 
in the sensitivity of the treatment effect in the high dimensional causal inference
as well as identifying confounder variables. However, indicator
based confounder selection can be deceptive, especially
when the predictor is strongly associated with either the treatment or 
the outcome, as this increases the posterior expectation of the selection
indicators. To avoid that, we apply a post-hoc selection scheme
which successfully removes negligible non-zero effects from the model,
attaining a smaller set of confounders. Finally, we illustrate
our method using a synthetic dataset.
\end{abstract}

@@

@@

Causal inference concerns estimating the causal
effect of independent variables on a dependent variable. Ideally,
randomised trials are the most efficient way to perform this task.
However, this is not always practical due to, for instance, ethical 
concerns, design cost, population size, to name a few. This
leaves us with observational studies
where data is collected though surveys or record keeping. But this
can be problematic in the presence of confounders, which are variables associated with both the treatment and the outcome.
In such cases, we must be extra cautious as we risk
unwanted bias in the treatment effect estimator \cite{rosenbaum83}.
Several authors have tackled the presence of
confounder variables. 
Robins \cite{Robins1986ANA} used a graphical
approach to identify the causal parameters.
Rosenbaum and Robin \cite{rosenbaum1985} suggested a link model to estimate
the propensity scores for all individuals. Subsequently, several other
methods have been proposed based on propensity score matching;
see \cite{winship99,stuart10} for a brief review.

@@

%%% MT to TB: check if you're happy with this paragraph
To decide whether or not to treat a new individual with given predictors,
we are mainly interested in the effect of the treatment on the outcome.
More precisely, the treatment effect of a new individual, indexed as $n+1$,
whose outcome $Y_{n+1}$ is not yet observed, and with observed predictors $X_{n+1}=x_{n+1}$, is defined by:
\begin{align}
  \delta(x_{n+1})
  &\coloneqq\mathbb{E}(Y_{n+1}\mid X_{n+1}=x_{n+1},T_{n+1} =1) - \mathbb{E}(Y_{n+1}\mid X_{n+1}=x_{n+1},T_{n+1}=0)
\end{align}
For our model, due to linearity of expectation, we have that
\begin{align}
  \delta(x_{n+1})
  &=\beta_T+x_{n+1}\beta+\mathbb{E}(\epsilon_{n+1}\mid X_{n+1}=x_{n+1},T_{n+1} =1) \\
  &\quad - x_{n+1}\beta-\mathbb{E}(\epsilon_{n+1}\mid X_{n+1}=x_{n+1},T_{n+1} =0)\\
  \intertext{and because $\epsilon_{n+1}$ is independent from $X_{n+1}$ and $T_{n+1}$,}
  &=\beta_{T}.
\end{align}
Note that, for this model, the treatment effect $\delta(x_{n+1})$
does not depend on the observed value $x_{n+1}$ of $X_{n+1}$.
So, to find the treatment effect, we simply need to estimate $\beta_T$.

@@

Now, for each fixed value of $q$, let $\hat{\beta}_{S(q)}$ be the posterior means 
of the regression coefficients of the outcome model with respect to
the predictors that belong to $S(q)$. Similarly,
let $\hat{\gamma}_{S(q)}$ be the posterior means of the regression
coefficients for the treatment effects. Since we use continuous 
spike and slab priors, these regression coefficients are not sparse.
Moreover, with our variable selection we only determine whether the variable 
is included in at least one of the models. But, we cannot determine a specific 
association. Therefore, to adjust the sparsity of the estimates and understand
the specific association with the treatment/outcome/both, we apply the 
``decoupled shrinkage and selection'' method proposed by \cite{hahn2015}. 
For that, we solve the following adaptive LASSO-type \cite{Zou2006}
problems

@@

For the simulation studies, we consider 2 different settings. In each
case, we generate the design matrix $X$ such that $X_i\sim\mathcal{N}(0, \Sigma)$
for $1\le i\le n$ where $\Sigma_{ij} = 0.3^{|i-j|}$. In this way, we 
generate 50 predictors for our model with mild correlations among them.
We then use the following distributions to generate the outcome and
the treatment indicator: 
\begin{equation}
    T_i \sim \text{Bernoulli}\left(1/(1+\exp(-X_i\gamma))\right)
    \quad\text{and}\quad
%%% MT to TB: did you forget to mention the error term in the next equation?
    Y_i = 4T_i + X_i\beta.
\end{equation}
%%% MT to BT: added this sentence for clarity later when discussing tables
Note that the simulated causal effect $\beta_T$ is equal to $4$.
\begin{description}
    \item[Scenario 1] --- $|\gamma_j|, |\beta_j|>0$ for $j\le 10$
    \item[Scenario 2] --- $|\gamma_j|>0$ for $j\le 10$ and $|\beta_j|>0$ for $j\le 15$
\end{description}
For both
the cases, we consider different numbers of observations $n$ where
$n=25+ 5k$ for $k=0,1,2,\dots,10$.

@@

\paragraph{Elicitation}
For the
elicitation of $\mathcal{P}$, we use the marginal correlation between 
$Y$ and $X$ to determine bounds on the number of active variables.
%%% MT to BT: I think we need to clarify what is going on here... What
%%% were the marginal correlations? How are these values 0.15 and 0.35
%%% informed from the marginal correlations? Also, why are marginal
%%% correlations the best way to do this? Ideally, one would set this
%%% without reference to the data... (since it is prior elicitation)
We set the thresholds to be $0.15$ and $0.35$ for the correlations.
We compute the
number of variables with marginal correlation greater than 0.15
(say $p_1$) and number of variables with  marginal 
correlation greater than 0.35 (say $p_2$). 
We use these numbers to obtain the bounds on the number of active
variables so that $\mathcal{P}=[p_2/p , p_1/p]$.

@@

\paragraph{Results}
\Cref{tab:causal} shows the results of estimating the causal effect $\beta_T$
For reference, recall the true value is $\beta_T=4$. 
As we perform a sensitivity analysis,
our method gives an interval estimate for the causal effect:
the first row gives the lower bound
and the second row gives the upper bound. We notice that our method is 
somewhat in agreement with the other methods but is more consistent
in terms of estimating the treatment effect. However, this is not the
case for other methods and sometimes those methods produce extreme 
values. This can be observed in \cref{fig:comp:trt} as well. Here, the true 
value is represented by the straight line for $\beta_T = 4$.

In these simulations, our method tends
to underestimate the causal effect.
%%% MT to TB: why is the problem with a? can you explain a bit more?
This suggests that
we may want to have a different value of $a$ for these sets of observations
%%% MT to TB: is the problem that it is "fixed"? this seems a bit misleading
instead of a fixed value of $a=10$ for all of our analyses.
We can also see that the lower bound tends to improve
with increasing number of observations: as we accumulate
more information, the interval becomes smaller and converges towards
the true value.

@@

\begin{figure}
    \centering
    \includegraphics[width = 0.9\linewidth]{RBCE_comp.pdf}
    \caption{Comparison of different methods in estimating the treatment effect.}
    \label{fig:comp:trt}
\end{figure}

%%% MT to TB: I changed "identification" to "selection" (assuming that is meant?)
For variable selection, we use a loss function as described earlier.
Here, we consider
$\ell_1=\ell_2=1$ and $\ell_3= 0.2$,
%%% MT to TB: I've briefly recap what these losses mean; please check if correct
i.e. we associate a loss of $1$ with false positive and false negative selections,
and a loss of $0.2$ with indeterminate selections.
Note that we could also choose more 
sophisticated loss functions based on \cite{ZAFFALON20121282}.
%%% MT to TB: I added "we sum these losses together across all preds"; check
We sum these losses together across all predictors
to obtain the total loss, presented in \cref{tab:misspec}.
The table counts the number of
false positives (FP) and false negatives (FN). For RBCE, we have an
additional column (ID)
which counts the number of indeterminate predictors.
From the table it can be seen that for the first scenario, our method
abstains from identifying some variables for 
$n <50$. Especially for $n=25$, our method identifies 26 and 23 variables as indeterminate
for the first setting and second setting respectively. However,
later on our method gives more precise results in terms of variable
selection. We also notice that BSSL tends to perform poorly
in terms of variable selection for $n=25$. This can be seen
from the causal effect estimation as well.
Moreover, we observe that for the second setting both SSCE
and BSSCE underperform in identifying the active variables, which can 
be explained from \cref{tab:causal} as well.

% latex table generated in R 4.3.0 by xtable 1.8-4 package
% Wed May 24 00:50:53 2023
\begin{table}[ht]
\caption{Loss based on misspecification of active variables in different
models.}\label{tab:misspec}
\centering
\subcaption*{First scenario: $|\gamma_j|, |\beta_j|>0$ for $j\le 10$}
\begin{tabular}{|c||rrr|r||rr|r||rr|r||rr|r|}
  \hline
  &\multicolumn{4}{c||}{RBCE}&\multicolumn{3}{c||}{SSCE}
  &\multicolumn{3}{c||}{BSSCE}&\multicolumn{3}{c|}{BSSL}\\
  \cline{2-14}
 Samples & FP & FN & ID & Tot & FP & FN & Tot & FP & FN & Tot & FP & FN & Tot \\ 
  \hline
25 &   0 &   0 &  26 & 5.2 & -- & -- & -- & -- & -- & -- &  12 &   2 & 14\\ 
  30 &   0 &   1 &   1 & 1.2 & -- & -- & -- & -- & -- & -- &   0 &   0 & 0\\ 
  35 &   0 &   0 &   1 & 0.2 & -- & -- & -- & -- & -- & -- &   0 &   0 & 0\\ 
  40 &   0 &   1 &   0 & 1.0 &-- & -- & -- & -- & -- & -- &   0 &   0 & 0\\ 
  45 &   0 &   0 &   1 & 0.2 & -- & -- & -- & -- & -- & -- &   0 &   0 & 0\\ 
  50 &   0 &   0 &   0 & 0.0 &  0 &   0  & 0 &   0 &   0  & 0 &   0 &   0  & 0\\ 
  55 &   0 &   0 &   0 & 0.0 &   0 &   0 &   0  & 0 &   0  & 0 &   0 &   0  & 0\\ 
  60 &   0 &   0 &   0 & 0.0 &   0 &   0 &   0 &   0  & 0  & 0 &   0 &   0  & 0\\ 
  65 &   0 &   0 &   0 & 0.0 &   0 &   0 &   0 &   0 &   0  & 0  & 0 &   0  & 0\\ 
  70 &   0 &   0 &   0 & 0.0 &   0 &   0 &   0 &   0 &   0  & 0  & 0 &   0  & 0\\ 
  75 &   0 &   0 &   0 & 0.0 &   0 &   0 &   0 &   0 &   0  & 0  & 0 &   0  & 0\\ 
   \hline
\end{tabular}
\subcaption*{Second scenario: $|\gamma_j|>0$ for $j\le 10$ and $|\beta_j|>0$ for $j\le 15$}
\begin{tabular}{|c||rrr|r||rr|r||rr|r||rr|r|}
  \hline
  &\multicolumn{4}{c||}{RBCE}&\multicolumn{3}{c||}{SSCE}
  &\multicolumn{3}{c||}{BSSCE}&\multicolumn{3}{c|}{BSSL}\\
  \cline{2-14}
 Samples & FP & FN & ID & Tot & FP & FN & Tot & FP & FN & Tot & FP & FN & Tot \\ 
  \hline
25 &   0 &   2 &  23 & 6.6 & -- & -- & -- & -- & -- & -- &   9 &   4 & 13\\ 
  30 &   0 &   2 &   9 & 3.8 & -- & -- & -- & -- & -- & -- &   0 &   0 & 0 \\ 
  35 &   0 &   0 &  18 & 3.6 & -- & -- & -- & -- & -- & -- &   0 &   0 & 0 \\ 
  40 &   0 &   0 &   5 & 1.0 &-- & -- & -- & -- & -- & -- &   0 &   0 & 0 \\ 
  45 &   0 &   0 &   3 & 0.6 & -- & -- & -- & -- & -- & -- &   0 &   0 & 0 \\ 
  50 &   0 &   0 &   1 & 0.2 &  0 &   7 & 7 &   0 &  14 & 14 &   0 &   0 & 0 \\ 
  55 &   0 &   0 &   1 & 0.2 &  0 &   0 & 0 &  0 &  12 & 12 &  0 &   0 & 0 \\ 
  60 &   0 &   0 &   1 & 0.2 &  1 &   0 & 1 &  0 &   0 &  0 & 0 &  0 &   0 \\ 
  65 &   0 &   0 &   0 & 0.0 &  0 &  12 & 12 &  0 &   0 &  0 & 0 &  0 &   0 \\ 
  70 &   0 &   0 &   0 & 0.0 &  0 &   0 &  0 &  0 &   0 &  0 & 0 &  0 &   0 \\ 
  75 &   0 &   0 &   0 & 0.0 &  0 &   0 &  0 &  0 &   0 &  0 & 0 &  0 &   0 \\ 
   \hline
\end{tabular}
\end{table}

>>>>

\begin{abstract}
Causal inference using observational data is important in
many fields, including epidemiology, social science, economics, and many more.
The goal of causal inference is to find the causal effect on the subjects
by identifying causal links between the variables and the outcome.
However, estimation of such causal links is extremely 
difficult because the causal effects may vary from subject 
to subject. Unfortunately, modelling the underlying heterogeneity explicitly makes the 
problem practically unsolvable. Additionally, for high dimensional problems,
we often need to find a subset of 
explanatory variables to initiate the treatment. However, current variable selection methods
simply tend to maximise the predictive performance of the outcome model. This can be problematic when information and data are limited,
as the consequence of mistreatment can be harmful. 
So, in this paper, we develop a model for causal inference using
robust Bayesian analysis, to allow for abstention when selecting
explanatory variables.
Our robust Bayesian model uses a set of spike and slab priors 
through prior elicitation to obtain robust estimates for
both the treatment and outcome model. We are specifically interested 
in the sensitivity of the causal effect in the high dimensional causal inference
as well as identifying confounder variables. However, indicator
based confounder selection can be deceptive, especially
when the predictor is strongly associated with either the treatment or 
the outcome, as this increases the posterior expectation of the selection
indicators. To avoid that, we apply a post-hoc selection scheme
which successfully removes negligible non-zero effects from the model,
attaining a smaller set of confounders. Finally, we illustrate
our method using a synthetic dataset.
\end{abstract}

@@

%TB to MT: changed to causal effect now

@@

Causal inference concerns estimating the causal
effect of independent variables on a dependent variable. Ideally,
randomised trials are the most efficient way to perform this task.
However, this is not always practical due to, for instance, ethical 
concerns, design cost, population size, to name a few. This
leaves us with observational studies
where data is collected though surveys or record keeping. But this
can be problematic in the presence of confounders, which are variables associated with both the treatment and the outcome.
In such cases, we must be extra cautious as we risk
unwanted bias in the causal effect estimator \cite{rosenbaum83}.
Several authors have tackled the presence of
confounder variables. 
Robins \cite{Robins1986ANA} used a graphical
approach to identify the causal parameters.
Rosenbaum and Robin \cite{rosenbaum1985} suggested a link model to estimate
the propensity scores for all individuals. Subsequently, several other
methods have been proposed based on propensity score matching;
see \cite{winship99,stuart10} for a brief review.

@@

%%% MT to TB: check if you're happy with this paragraph
To decide whether or not to treat a new individual with given predictors,
we are mainly interested in the effect of the treatment on the outcome.
More precisely, the causal effect of a new individual, indexed as $n+1$,
whose outcome $Y_{n+1}$ is not yet observed, and with observed predictors $X_{n+1}=x_{n+1}$, is defined by:
\begin{align}
  \delta(x_{n+1})
  &\coloneqq\mathbb{E}(Y_{n+1}\mid X_{n+1}=x_{n+1},T_{n+1} =1) - \mathbb{E}(Y_{n+1}\mid X_{n+1}=x_{n+1},T_{n+1}=0)
\end{align}
For our model, due to linearity of expectation, we have that
\begin{align}
  \delta(x_{n+1})
  &=\beta_T+x_{n+1}\beta+\mathbb{E}(\epsilon_{n+1}\mid X_{n+1}=x_{n+1},T_{n+1} =1) \\
  &\quad - x_{n+1}\beta-\mathbb{E}(\epsilon_{n+1}\mid X_{n+1}=x_{n+1},T_{n+1} =0)\\
  \intertext{and because $\epsilon_{n+1}$ is independent from $X_{n+1}$ and $T_{n+1}$,}
  &=\beta_{T}.
\end{align}
Note that, for this model, the causal effect $\delta(x_{n+1})$
does not depend on the observed value $x_{n+1}$ of $X_{n+1}$.
So, to find the causal effect, we simply need to estimate $\beta_T$.

@@

Now, for each fixed value of $q$, let $\hat{\beta}_{S(q)}$ be the posterior means 
of the regression coefficients of the outcome model with respect to
the predictors that belong to $S(q)$. Similarly,
let $\hat{\gamma}_{S(q)}$ be the posterior means of the regression
coefficients for the causal effects. Since we use continuous 
spike and slab priors, these regression coefficients are not sparse.
Moreover, with our variable selection we only determine whether the variable 
is included in at least one of the models. But, we cannot determine a specific 
association. Therefore, to adjust the sparsity of the estimates and understand
the specific association with the treatment/outcome/both, we apply the 
``decoupled shrinkage and selection'' method proposed by \cite{hahn2015}. 
For that, we solve the following adaptive LASSO-type \cite{Zou2006}
problems

@@

For the simulation studies, we consider 4 different settings. In each
case, we generate the design matrix $X$ such that $X_i\sim\mathcal{N}(0, \Sigma)$
for $1\le i\le n$ where $\Sigma_{ij} = 0.3^{|i-j|}$. In this way, we 
generate predictors for our model with mild correlations among (within?) them.
We then use the following distributions to generate the outcome and
the treatment indicator: 
\begin{equation}
    T_i \sim \text{Bernoulli}\left(1/(1+\exp(-X_i\gamma))\right)
    \quad\text{and}\quad
%%% MT to TB: did you forget to mention the error term in the next equation? 
%%% TB to MT: Thanks Matthias, yes I forgot to put that. 
    Y_i = 4T_i + X_i\beta + \epsilon_i.
\end{equation}
%%% MT to BT: added this sentence for clarity later when discussing tables
Note that the simulated causal effect $\beta_T$ is equal to $4$.
\begin{description}
    \item[Scenario 1] --- $|\gamma_j|, |\beta_j|>0$ for $j\le 10$
    \item[Scenario 2] --- $|\gamma_j|>0$ for $j\le 10$ and $|\beta_j|>0$ for $j\le 15$
\end{description}
For both
the cases, we consider different numbers of observations $n$ where
$n=25+ 5k$ for $k=0,1,2,\dots,35$ and 50 ($p$)
predictors. This way, we check the efficiency of our method with varying level of information.

For the next two cases, we check our method for varying number of predictors (and hence sparsity level, ie the percentage of active variables present in the model)

\begin{description}
    \item[Scenario 3] --- $|\gamma_j|, |\beta_j|>0$ for $j\le 10$
    \item[Scenario 4] --- $|\gamma_j|>0$ for $j\le 10$ and $|\beta_j|>0$ for $j\le 15$
\end{description}
For both
the cases, we consider different numbers of predictors $p$ where
$p=25+ 5k$ for $k=1,2,\dots,35$ and 100 ($n$)
predictors.

@@

\paragraph{Elicitation}
For the
elicitation of $\mathcal{P}$, we use the marginal correlation between 
$Y$ and $X$ to determine bounds on the number of active variables.
%%% MT to BT: I think we need to clarify what is going on here... What
%%% were the marginal correlations? How are these values 0.15 and 0.35
%%% informed from the marginal correlations? Also, why are marginal
%%% correlations the best way to do this? Ideally, one would set this
%%% without reference to the data... (since it is prior elicitation)
%%% TB to MT: To be honest it was just two random numbers I came up with, without any proper reason so that the this doesn't become an overfit

We set the thresholds to be $0.15$ and $0.35$ for the correlations.
We compute the
number of variables with marginal correlation greater than 0.15
(say $p_1$) and number of variables with  marginal 
correlation greater than 0.35 (say $p_2$). 
We use these numbers to obtain the bounds on the number of active
variables so that $\mathcal{P}=[p_2/p , p_1/p]$.

@@

\paragraph{Results}
\Cref{tab:causal} shows the results of estimating the causal effect $\beta_T$
For reference, recall the true value is $\beta_T=4$. 
As we perform a sensitivity analysis,
our method gives an interval estimate for the causal effect:
the first row gives the lower bound
and the second row gives the upper bound. We notice that our method is 
somewhat in agreement with the other methods but is more consistent
in terms of estimating the causal effect. However, this is not the
case for other methods and sometimes those methods produce extreme 
values. This can be observed in \cref{fig:comp:trt} as well. Here, the true 
value is represented by the straight line for $\beta_T = 4$.

In these simulations, our method tends
to underestimate the causal effect.
%%% MT to TB: why is the problem with a? can you explain a bit more?
This suggests that
we may want to have a different value of $a$ for these sets of observations
%%% MT to TB: is the problem that it is "fixed"? this seems a bit misleading
%TB to MT: I was thinking of a differernt value to get a flatter prior
instead of a fixed value of $a=10$ for all of our analyses.
We can also see that the lower bound tends to improve
with increasing number of observations: as we accumulate
more information, the interval becomes smaller and converges towards
the true value.

@@

\begin{figure}
    \centering
    \includegraphics[width = 0.9\linewidth]{treat_obs.pdf}
    \caption{Comparison of different methods in estimating the causal effect for varying number of observations.}
    \label{fig:comp:trt}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width = 0.9\linewidth]{treat_pred.pdf}
    \caption{Comparison of different methods in estimating the causal effect for varying number of predictors.}
    \label{fig:comp:trt:pred}
\end{figure}

%%% MT to TB: I changed "identification" to "selection" (assuming that is meant?)
% TB to MT: yes, thanks
For variable selection, we use a loss function as described earlier.
Here, we consider
$\ell_1=\ell_2=1$ and $\ell_3= 0.2$,
%%% MT to TB: I've briefly recap what these losses mean; please check if correct
% TB to MT: yes, thanks
i.e. we associate a loss of $1$ with false positive and false negative selections,
and a loss of $0.2$ with indeterminate selections.
Note that we could also choose more 
sophisticated loss functions based on \cite{ZAFFALON20121282}.
%%% MT to TB: I added "we sum these losses together across all preds"; check
% TB to MT: yes, thanks
We sum these losses together across all predictors
to obtain the total loss, presented in \cref{tab:misspec}.
The table counts the number of
false positives (FP) and false negatives (FN). For RBCE, we have an
additional column (ID)
which counts the number of indeterminate predictors.
From the table it can be seen that for the first scenario, our method
abstains from identifying some variables for 
$n <50$. Especially for $n=25$, our method identifies 26 and 23 variables as indeterminate
for the first setting and second setting respectively. However,
later on our method gives more precise results in terms of variable
selection. We also notice that BSSL tends to perform poorly
in terms of variable selection for $n=25$. This can be seen
from the causal effect estimation as well.
Moreover, we observe that for the second setting both SSCE
and BSSCE underperform in identifying the active variables, which can 
be explained from \cref{tab:causal} as well.

% latex table generated in R 4.3.0 by xtable 1.8-4 package
% Wed May 24 00:50:53 2023
\begin{table}[ht]
\caption{Loss based on misspecification of active variables in different
models.}\label{tab:misspec}
\centering
\subcaption*{First scenario: $|\gamma_j|, |\beta_j|>0$ for $j\le 10$}
\begin{tabular}{|c||rrr|r||rr|r||rr|r||rr|r|}
  \hline
  &\multicolumn{4}{c||}{RBCE}&\multicolumn{3}{c||}{SSCE}
  &\multicolumn{3}{c||}{BSSCE}&\multicolumn{3}{c|}{BSSL}\\
  \cline{2-14}
 Samples & FP & FN & ID & Tot & FP & FN & Tot & FP & FN & Tot & FP & FN & Tot \\ 
  \hline
1 &   0 &   0 &  43 &  &  &  &  &   0 &   0 \\ 
  2 &   0 &   0 &   5 &  &  &  &  &   0 &   0 \\ 
  3 &   0 &   0 &   2 &  &  &  &  &   0 &   0 \\ 
  4 &   0 &   0 &   0 &  &  &  &  &   0 &   0 \\ 
  5 &   0 &   0 &   0 &  &  &  &  &   0 &   0 \\ 
  6 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  7 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  8 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  9 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  10 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  11 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  12 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  13 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  14 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  15 &   0 &   0 &   0 &   1 &   0 &   0 &   0 &   0 &   0 \\ 
  16 &   0 &   0 &   0 &   1 &   0 &   0 &   0 &   0 &   0 \\ 
  17 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  18 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  19 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  20 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  21 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  22 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  23 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  24 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  25 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  26 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  27 &   0 &   0 &   0 &   1 &   0 &   0 &   0 &   0 &   0 \\ 
  28 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  29 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  30 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  31 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  32 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  33 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  34 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  35 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  36 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
   \hline
\end{tabular}
\end{table}
\begin{table}
\caption{Second scenario: $|\gamma_j|>0$ for $j\le 10$ and $|\beta_j|>0$ for $j\le 15$}
\begin{tabular}{|c||rrr|r||rr|r||rr|r||rr|r|}
  \hline
  &\multicolumn{4}{c||}{RBCE}&\multicolumn{3}{c||}{SSCE}
  &\multicolumn{3}{c||}{BSSCE}&\multicolumn{3}{c|}{BSSL}\\
  \cline{2-14}
 Samples & FP & FN & ID & Tot & FP & FN & Tot & FP & FN & Tot & FP & FN & Tot \\ 
  \hline
1 &   0 &   1 &  21 &  &  &  &  &   0 &   0 \\ 
  2 &   0 &   0 &  44 &  &  &  &  &   0 &  13 \\ 
  3 &   0 &   0 &  11 &  &  &  &  &   0 &  13 \\ 
  4 &   0 &   0 &   4 &  &  &  &  &   0 &   0 \\ 
  5 &   0 &   0 &   3 &  &  &  &  &   0 &   0 \\ 
  6 &   0 &   0 &   2 &   0 &   0 &   0 &  15 &   0 &   0 \\ 
  7 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  8 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  9 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  10 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  11 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  12 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  13 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  14 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  15 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  16 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  17 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  18 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  19 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  20 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  21 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  22 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  23 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  24 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  25 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  26 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  27 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  28 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  29 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  30 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  31 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  32 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  33 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  34 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  35 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
  36 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 &   0 \\ 
   \hline
\end{tabular}
\end{table}
